\begin{thebibliography}{99}

\bibitem{mccloskey1989}
M.\ McCloskey and N.\ J.\ Cohen.
\newblock Catastrophic interference in connectionist networks: The sequential
learning problem.
\newblock \emph{Psychology of Learning and Motivation}, 24:109--165, 1989.

\bibitem{kirkpatrick2017}
J.\ Kirkpatrick et al.
\newblock Overcoming catastrophic forgetting in neural networks.
\newblock \emph{Proceedings of the National Academy of Sciences},
114(13):3521--3526, 2017.

\bibitem{zenke2017}
F.\ Zenke, B.\ Poole, and S.\ Ganguli.
\newblock Continual learning through synaptic intelligence.
\newblock \emph{ICML}, 2017.

\bibitem{stern2022}
M.\ Stern, D.\ Hexner, J.\ W.\ Rocks, and A.\ J.\ Liu.
\newblock Supervised learning through physical changes in a mechanical system.
\newblock \emph{Physical Review X}, 12:031044, 2022.

\bibitem{stern2024}
M.\ Stern, A.\ J.\ Liu, and V.\ Balasubramanian.
\newblock Physical learning beyond the quasistatic limit.
\newblock \emph{Physical Review Research}, 6:013004, 2024.

\bibitem{scellier2017}
B.\ Scellier and Y.\ Bengio.
\newblock Equilibrium propagation: Bridging the gap between energy-based
models and backpropagation.
\newblock \emph{Frontiers in Computational Neuroscience}, 11:24, 2017.

\bibitem{thresholdedphysical2025}
Authors.
\newblock Thresholded local updates in tunable physical networks for
sequential learning.
\newblock \emph{arXiv:2512.03799}, 2025.

\bibitem{izmailian2014}
N.\ Sh.\ Izmailian and R.\ Kenna.
\newblock A generalised formulation of the Laplacian approach to resistor
networks.
\newblock \emph{arXiv preprint arXiv:1406.5045}, 2014.

\bibitem{lin2026}
J.\ Lin, A.\ Desai, F.\ Barrows, and F.\ Caravelli.
\newblock How to Train Your Resistive Network: Generalized Equilibrium
Propagation and Analytical Learning.
\newblock \emph{arXiv preprint arXiv:2602.03546}, 2026.

\end{thebibliography}
